Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Add the relation between coclassification and phylogeny to the results.

\begin{figure}
	\centering
	\begin{forest} phylogeny
		[
			[
				[
					[\emph{D. simulans}]
					[\emph{D. birchii}]
				]
				[
					[\emph{D. pandora}]
					[\emph{D. pseudoananassae}]
				]
			]
			[
				[
					[\emph{D. pallidifrons}]
					[\emph{D. sulfurigaster}]
				]
			]
		]
	\end{forest}

@@

>>>>

\begin{figure}
	\centering
	\begin{forest} phylogeny
		[
			[
				[
					[\emph{D. simulans}]
					[\emph{D. birchii}]
				]
				[
					[\emph{D. pandora}]
					[\emph{D. pseudoananassae}]
				]
			]
			[
				[
					[\emph{D. pallidifrons}]
					[\emph{D. sulfurigaster}]
				]
			]
		]
	\end{forest}
	%TODO: Mark subgroups and subgenuses on the diagram.

@@

A high likelihood of coclassifcation was associated with phylogeny in one instance, but by no means consistently.
The phylogeny divides the six spcies into three most closely related pairs (\cref{fig:phylogeny}).
The pair of \emph{D. pallidifrons} and \emph{D. sulfurigaster}, which both belonged to a different subgenus than the other four species, were also the only pair of species to be coclassified with relatively high probability in both the row and column groupings.
In constrast, each of the other pairs were coclassified with very low probabilities in both the row and column groupings.
Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the row groupings frequently coclassified \emph{D. sulfurigaster} and \emph{D. simulans}, while the column groupings frequently coclassified both \emph{D. pallidifrons} and \emph{D. sulfurigaster} of the Drosophila subgenus with \emph{D. birchii} of the Sophophora subgenus.
